Composable Concurrency Abstractions

### 2016-09-15 annotated-bibliography/annotated-bibliography.tex
Added new finds to bibliography

\begin{abstract}
A wide variety of concurrency models presents challenges in both performance and composability. By identifying common concepts and techniques, a high-level language virtual machine can support a variety of abstractions at a low level, and different models can be used in tandem with each other.
\end{abstract}

>>>>

\begin{abstract}
Varied concurrency models and implementations present challenges in both performance and composability. By identifying common concepts and techniques, a high-level language virtual machine can support a variety of abstractions at a low level, and different models can be used in tandem.
\end{abstract}
